### 2017-06-14 sheets/talk-7/sheet-7.tex

\section{Limits}

@@

\begin{exercise}[Contained limit]
  Let $D$ be a diagram.
  Find an example of a limit $L$ that is completely contained in $D$,
  meaning the vertex of $L$ is in the image of $D$.
\end{exercise}

@@

\begin{exercise}[Cones as natural transformations]
  Let $\mathscr{C}$ and $\bf{I}$ be any categories, $D : \bf{I} \to \mathscr{C}$ a diagram.
  Verify that a natural transformation $\pi : \Updelta_v \to D(\bf{I})$ is a cone over $D$ with vertex $V$.
\end{exercise}

>>>>

@@

@@

\begin{exercise}[Cones as natural transformations]
  Let $\mathscr{C}$ and $\bf{I}$ be any categories, $D : \bf{I} \to \mathscr{C}$ a diagram.
  Verify that a natural transformation $\pi : \Updelta_V \to D(\bf{I})$ is a cone over $D$ with vertex $V$.
\end{exercise}
